---
title: "Forecast Evaluation for the German Forecast Hub"
output: 
  html_document
# toc: true
# toc_float: true
# toc_collapsed: true
# toc_depth: 3
---

  
```{r setup, include=FALSE}
# packages
library(scoringutils)
library(magrittr)
library(knitr)

# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, 
                      out.width = "100%")

# source other functions
source("load-data.R")

# evaluation options
models <- "all" # models to evaluate
root_dir <- "../data-processed" # root directory for the submission files
load_from_server <- FALSE
locations <- c("Germany", "Poland")
forecast_dates <- c("2020-10-12", "2020-10-19", "2020-10-26", "2020-11-02", 
                    "2020-11-09")




```

``` {r helper-functions}
# filter data
filter_helper <- function(dataframe, forecast_date = NULL, location = NULL) {
  if (!is.null(forecast_date)) {
    forecast_date <- forecast_date # why do I need this?
    dataframe <- dplyr::filter(dataframe, 
                               forecast_date == {{forecast_date}})
  }
  if (!is.null(location)) {
    location <- location # and this?
    dataframe <- dplyr::filter(dataframe, 
                               location_name == {{location}})
  }
  return(dataframe)
}

# # make visualisation with correct structure
# report_sub_part <- function(plot_function, 
#                             case_data, 
#                             death_data,
#                             forecast_dates = NULL, 
#                             locations = NULL) {
#   if (is.null(locations)) {
#   locations <- case_data$location_name %>%
#     unique()
# }
# 
# for (location in locations) {
#   
#   cat("\n\n##", location, "{.tabset}\n")
#   
#   if (is.null(forecast_dates)) {
#     forecast_dates <- case_data %>%
#       dplyr::filter(location_name == {{ location }}) %>%
#       dplyr::pull(forecast_date) %>%
#       unique()
#   }
#   
#   for (forecast_date in forecast_dates) {
#     cases <- filter_helper(case_data_w_pred, forecast_date, location)
#     deaths <- filter_helper(death_data_w_pred, forecast_date, location)
#     
#     if (nrow(cases) == 0 & nrow(deaths) == 0) {
#       next()
#     } 
#     
#     if (nrow(cases) != 0) {
#       cat(paste0("### ", forecast_date), "\n")
#       
#       p1 <- plot_predictions_helper(data = cases, additional_data = obs_case, 
#                                     location = location, type = "cases")
#       print(p1)
#       cat("\n\n\n")
#     }
# 
#     if (nrow(deaths) != 0) {
#       
#       if (nrow(cases) == 0) {
#         cat(paste0("### ", forecast_date), "\n")
#       }
#       
#       p2 <-plot_predictions_helper(data = deaths, additional_data = obs_death, 
#                                     location = location, type = "deaths") 
#       print(p2)
#     }
#     
#     cat("\n\n")
#     
#   }
# }
#   
#   
# }


```



This is a preliminary evaluation of forecasts made for the [German Forecast Hub](https://github.com/KITmetricslab/covid19-forecast-hub-de). These evaluations are preliminary - this means I cannot currently rule out any mistakes and the plots and analyses are subject to change. The evaluations are not authorised by the German Forecast Hub team. 

Feel free to reproduce this analysis. To that end, you can clone this repository and the Forecast Hub repository, specify the directory of the submissions files in the R-Markdown script and run the script. 

If you have questions or want to give feedback, please create an issue in this repository. 

```{r load-data, results = 'asis'}

# load predictions (i.e. load submission files)
pred <- load_submission_files(dates = forecast_dates,
                              models = models,
                              dir = root_dir) %>%
  dplyr::filter(target_end_date >= "2020-10-17") %>%
  dplyr::select(-location)


if (load_from_server) {
  get_data(load_from_server = TRUE, 
           country = "Germany_Poland")
}

obs_death <- get_data(cases = FALSE)
obs_case <- get_data()


case_data_w_pred <- dplyr::left_join(pred %>%
                                       dplyr::rename(prediction = value) %>%
                                       dplyr::filter(grepl("inc", target),
                                                     grepl("case", target),
                                                     type == "quantile"),
                                     obs_case %>%
                                       dplyr::rename(true_value = value))

case_data <- case_data_w_pred %>%
  dplyr::filter(!is.na(true_value))

death_data_w_pred <- dplyr::left_join(pred %>%
                                        dplyr::rename(prediction = value) %>%
                                        dplyr::filter(grepl("inc", target),
                                                      grepl("death", target),
                                                      type == "quantile"),
                                      obs_death %>%
                                        dplyr::rename(true_value = value))

death_data <- death_data_w_pred %>%
  dplyr::filter(!is.na(true_value))

```






# Forecast Visualisation

``` {r showdata, results = 'asis', warning = FALSE, fig.width = 10, eval = TRUE}
plot_predictions_helper <- function(data, additional_data, 
                                    n_weeks = 12, location, 
                                    type) {
  
  location <- location
  
  plot <- scoringutils::plot_predictions(data,
                                         x = "target_end_date", 
                                         facet_formula = ~ model, 
                                         add_truth_data = additional_data %>%
                                           dplyr::rename(true_value = value) %>%
                                           dplyr::filter(as.Date(target_end_date) >= (Sys.Date() - n_weeks * 7),
                                                         location_name == {{ location }}),
                                         scales = "free") +
    ggplot2::ggtitle(paste("Predictions for incident", type,  "in", location))
  
  return(plot)
}
 

if (is.null(locations)) {
  locations <- case_data$location_name %>%
    unique()
}

for (location in locations) {
  
  cat("\n\n##", location, "{.tabset}\n")
  
  if (is.null(forecast_dates)) {
    forecast_dates <- case_data %>%
      dplyr::filter(location_name == {{ location }}) %>%
      dplyr::pull(forecast_date) %>%
      unique()
  }
  
  for (forecast_date in forecast_dates) {
    cases <- filter_helper(case_data_w_pred, forecast_date, location)
    deaths <- filter_helper(death_data_w_pred, forecast_date, location)
    
    if (nrow(cases) == 0 & nrow(deaths) == 0) {
      next()
    } 
    
    if (nrow(cases) != 0) {
      cat(paste0("### ", forecast_date), "\n")
      
      p1 <- plot_predictions_helper(data = cases, additional_data = obs_case, 
                                    location = location, type = "cases")
      print(p1)
      cat("\n\n\n")
    }

    if (nrow(deaths) != 0) {
      
      if (nrow(cases) == 0) {
        cat(paste0("### ", forecast_date), "\n")
      }
      
      p2 <-plot_predictions_helper(data = deaths, additional_data = obs_death, 
                                    location = location, type = "deaths") 
      print(p2)
    }
    
    cat("\n\n")
    
  }
}


```

# Score Overview

Overview of all the models and metrics

``` {r scoretable, fig.width = 12, results = 'asis', eval = TRUE}
# overall summary
plot_score_table_helper <- function(data, type) {
  scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = "model")
  
  plot <- scoringutils::score_table(scores) + 
        ggplot2::ggtitle(paste("Incident", type))
  return(plot)
}

cat("\n\n## Overall")

pp <- plot_score_table_helper(dplyr::bind_rows(case_data, death_data), 
                              type = "cases and deaths together")
print(pp)

cat("\n\n## Overall cases and deaths separate")

p1 <- plot_score_table_helper(case_data, type = "cases")
print(p1)

cat("\n")

p2 <- plot_score_table_helper(death_data, type = "deaths")
print(p2)

cat("\n\n")


# by location
for (location in locations) {
  
  cat("\n\n##", location, "{.tabset}\n")
  
  cat(paste0("### Overall \n"))
  cases <- filter_helper(case_data, location = location)
  p1 <- plot_score_table_helper(data = cases, type = "cases")
  print(p1)
  
  cat("\n")
  
  deaths <- filter_helper(death_data, location = location)
  p2 <- plot_score_table_helper(data = deaths, type = "deaths")
  print(p2)
  
  cat("\n\n")
  
  
  for (forecast_date in forecast_dates) {
    cases <- filter_helper(case_data, location = location, 
                           forecast_date = forecast_date)
    deaths <- filter_helper(death_data, location = location, 
                            forecast_date = forecast_date)
    
    if (nrow(cases) == 0 & nrow(deaths) == 0) {
      next()
    } 
    
    if (nrow(cases) != 0) {
      cat(paste0("### ", forecast_date), "\n")
      p1 <- plot_score_table_helper(data = cases, type = "cases")
      print(p1)
    }
    
    cat("\n\n\n")
    
    if (nrow(deaths) != 0) {
      
      if (nrow(cases) == 0) {
        cat(paste0("### ", forecast_date), "\n")
      }
      p2 <- plot_score_table_helper(data = deaths, type = "deaths")
      print(p2)
    }
    
    cat("\n\n")
    
  }
}

```


## Interval Score Components

Weighted interval score broken down into its components "overprediction penalty", 
"underprediction penalty" and "sharpness"

``` {r wis-components, fig.width = 12, results = 'asis', eval = TRUE}
# overall summary
plot_wis_components_helper <- function(data, type) {
  scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = "model")
  
  plot <- scoringutils::wis_components(scores) + 
        ggplot2::ggtitle(paste("WIS componentents - Incident", type))
  return(plot)
}

plot_function <- plot_wis_components_helper

out <- knitr::knit_child("templates/overall-location-forecast_date.Rmd",
                         envir = environment()) 

cat(paste(out, collapse = '\n'))

# 
# cat("\n\n## Overall")
# 
# p1 <- plot_wis_components_helper(case_data, type = "cases")
# print(p1)
# 
# cat("\n")
# 
# p2 <- plot_wis_components_helper(death_data, type = "deaths")
# print(p2)
# 
# cat("\n\n")
# 
# 
# # by location
# for (location in locations) {
#   
#   cat("\n\n##", location, "{.tabset}\n")
#   
#   cat(paste0("### Overall \n"))
#   cases <- filter_helper(case_data, location = location)
#   p1 <- plot_wis_components_helper(data = cases, type = "cases")
#   print(p1)
#   
#   cat("\n")
#   
#   deaths <- filter_helper(death_data, location = location)
#   p2 <- plot_wis_components_helper(data = deaths, type = "deaths")
#   print(p2)
#   
#   cat("\n\n")
#   
#   
#   for (forecast_date in forecast_dates) {
#     cases <- filter_helper(case_data, location = location, 
#                            forecast_date = forecast_date)
#     deaths <- filter_helper(death_data, location = location, 
#                             forecast_date = forecast_date)
#     
#     if (nrow(cases) == 0 & nrow(deaths) == 0) {
#       next()
#     } 
#     
#     if (nrow(cases) != 0) {
#       cat(paste0("### ", forecast_date), "\n")
#       p1 <- plot_wis_components_helper(data = cases, type = "cases")
#       print(p1)
#     }
#     
#     cat("\n\n\n")
#     
#     if (nrow(deaths) != 0) {
#       
#       if (nrow(cases) == 0) {
#         cat(paste0("### ", forecast_date), "\n")
#       }
#       p2 <- plot_wis_components_helper(data = deaths, type = "deaths")
#       print(p2)
#     }
#     
#     cat("\n\n")
#     
#   }
# }

```


# Calibration

## Interval Coverage
Plot of the percentage of true values captured by each prediction interval

``` {r fig.width = 12, results = 'asis', eval = TRUE}




# overall summary
plot_interval_coverage_helper <- function(data, type) {
  scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = c("model", "range"))
  
  plot <- scoringutils::interval_coverage(scores) + 
        ggplot2::ggtitle(paste("Interval coverage - Incident", type))
  return(plot)
}

cat("\n\n## Overall")

p1 <- plot_interval_coverage_helper(case_data, type = "cases")
print(p1)

cat("\n")

p2 <- plot_interval_coverage_helper(death_data, type = "deaths")
print(p2)

cat("\n\n")


# by location
for (location in locations) {
  
  cat("\n\n##", location, "{.tabset}\n")
  
  cat(paste0("### Overall \n"))
  cases <- filter_helper(case_data, location = location)
  p1 <- plot_interval_coverage_helper(data = cases, type = "cases")
  print(p1)
  
  cat("\n")
  
  deaths <- filter_helper(death_data, location = location)
  p2 <- plot_interval_coverage_helper(data = deaths, type = "deaths")
  print(p2)
  
  cat("\n\n")
  
  for (forecast_date in forecast_dates) {
    cases <- filter_helper(case_data, location = location, 
                           forecast_date = forecast_date)
    deaths <- filter_helper(death_data, location = location, 
                            forecast_date = forecast_date)
    
    if (nrow(cases) == 0 & nrow(deaths) == 0) {
      next()
    } 
    
    if (nrow(cases) != 0) {
      cat(paste0("### ", forecast_date), "\n")
      p1 <- plot_interval_coverage_helper(data = cases, type = "cases")
      print(p1)
    }
    
    cat("\n\n\n")
    
    if (nrow(deaths) != 0) {
      
      if (nrow(cases) == 0) {
        cat(paste0("### ", forecast_date), "\n")
      }
      p2 <- plot_interval_coverage_helper(data = deaths, type = "deaths")
      print(p2)
    }
    
    cat("\n\n")
    
  }
}

```



## Quantile Coverage
Plot of the percentage of true values below each predictive quantile level

``` {r fig.width = 12, results = 'asis', eval = TRUE}

# overall summary
plot_quantile_coverage_helper <- function(data, type) {
  scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = c("model", "quantile"))
  
  plot <- scoringutils::quantile_coverage(scores) + 
        ggplot2::ggtitle(paste("Interval coverage - Incident", type))
  return(plot)
}

cat("\n\n## Overall")

p1 <- plot_quantile_coverage_helper(case_data, type = "cases")
print(p1)

cat("\n")

p2 <- plot_quantile_coverage_helper(death_data, type = "deaths")
print(p2)

cat("\n\n")


# by location
for (location in locations) {
  
  cat("\n\n##", location, "{.tabset}\n")
  
  cat(paste0("### Overall \n"))
  cases <- filter_helper(case_data, location = location)
  p1 <- plot_quantile_coverage_helper(data = cases, type = "cases")
  print(p1)
  
  cat("\n")
  
  deaths <- filter_helper(death_data, location = location)
  p2 <- plot_quantile_coverage_helper(data = deaths, type = "deaths")
  print(p2)
  
  cat("\n\n")
  
  for (forecast_date in forecast_dates) {
    cases <- filter_helper(case_data, location = location, 
                           forecast_date = forecast_date)
    deaths <- filter_helper(death_data, location = location, 
                            forecast_date = forecast_date)
    
    if (nrow(cases) == 0 & nrow(deaths) == 0) {
      next()
    } 
    
    if (nrow(cases) != 0) {
      cat(paste0("### ", forecast_date), "\n")
      p1 <- plot_quantile_coverage_helper(data = cases, type = "cases")
      print(p1)
    }
    
    cat("\n\n\n")
    
    if (nrow(deaths) != 0) {
      
      if (nrow(cases) == 0) {
        cat(paste0("### ", forecast_date), "\n")
      }
      p2 <- plot_quantile_coverage_helper(data = deaths, type = "deaths")
      print(p2)
    }
    
    cat("\n\n")
    
  }
}
  
```


# Bias {.tabset}

``` {r bias, fig.width = 12, results = 'asis', eval = TRUE}

plot_bias_helper <- function(data, type) {
  scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = c("model", "location_name"))
  
  plot <- scoringutils::score_heatmap(scores, metric = "bias", x = "location_name") + 
    ggplot2::labs(x = "Location") + 
    ggplot2::ggtitle(paste("Bias - Incident", type))
  return(plot)
}


cat(paste0("## Overall \n"))
cases <- case_data
p1 <- plot_bias_helper(data = cases, type = "cases")
print(p1)

cat("\n")

deaths <- death_data
p2 <- plot_bias_helper(data = deaths, type = "deaths")
print(p2)

cat("\n\n")

for (forecast_date in forecast_dates) {
  cases <- filter_helper(case_data, forecast_date = forecast_date)
  deaths <- filter_helper(death_data, forecast_date = forecast_date)
  
  if (nrow(cases) == 0 & nrow(deaths) == 0) {
    next()
  } 
  
  if (nrow(cases) != 0) {
    cat(paste0("## ", forecast_date), "\n")
    p1 <- plot_bias_helper(data = cases, type = "cases")
    print(p1)
  }
  
  cat("\n\n\n")
  
  if (nrow(deaths) != 0) {
    
    if (nrow(cases) == 0) {
      cat(paste0("## ", forecast_date), "\n")
    }
    p2 <- plot_bias_helper(data = deaths, type = "deaths")
    print(p2)
  }
  
  cat("\n\n")
  
}

```




