---
title: "Forecast Evaluation for the German Forecast Hub"
output: 
  github_document: default
  html_document: default
---

  
```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.show = "hold", 
                      out.width = "100%")

# packages
library(scoringutils)
library(magrittr)

# source other functions
source("load-data.R")

# evaluation options
models <- "all" # models to evaluate
root_dir <- "../data-processed" # root directory for the submission files
load_from_server <- FALSE

```

This is a preliminary evaluation of forecasts made for the [German Forecast Hub](https://github.com/KITmetricslab/covid19-forecast-hub-de). These evaluations are preliminary - this means I cannot currently rule out any mistakes and the plots and analyses are subject to change. The evaluations are not authorised by the German Forecast Hub team. 

Feel free to reproduce this analysis. To that end, you can clone this repository and the Forecast Hub repository, specify the directory of the submissions files in the R-Markdown script and run the script. 

If you have questions or want to give feedback, please create an issue in this repository. 

```{r load-data}

# load predictions (i.e. load submission files)
pred <- load_submission_files(num_last = 2,
                              models = models,
                              dir = root_dir) %>%
  dplyr::filter(target_end_date >= "2020-10-17") %>%
  dplyr::select(-location)


if (load_from_server) {
  get_data(load_from_server = TRUE, 
           country = "Germany_Poland")
}

obs_death <- get_data(cases = FALSE)
obs_case <- get_data()


case_data <- dplyr::inner_join(pred %>%
                              dplyr::rename(prediction = value) %>%
                              dplyr::filter(grepl("inc", target),
                                            grepl("case", target),
                                            type == "quantile"),
                            obs_case %>%
                              dplyr::rename(true_value = value))

death_data <- dplyr::inner_join(pred %>%
                              dplyr::rename(prediction = value) %>%
                              dplyr::filter(grepl("inc", target),
                                            grepl("death", target),
                                            type == "quantile"),
                            obs_death %>%
                              dplyr::rename(true_value = value))



```


## Forecast Visualisation

Visualisation of one week ahead forecasts

``` {r fig.show = "hold", out.width = "100%"}
scoringutils::plot_predictions(case_data %>%
                                 dplyr::filter(horizon == 1, 
                                               location_name == "Germany"),
                               x = "target_end_date", 
                               facet_formula = ~ model, 
                               scales = "fixed") + 
  ggplot2::ggtitle("One week ahead predictions for incident cases in Germany")


scoringutils::plot_predictions(case_data %>%
                                 dplyr::filter(horizon == 1, 
                                               location_name == "Poland"),
                               x = "target_end_date", 
                               facet_formula = ~ model, 
                               scales = "fixed") + 
  ggplot2::ggtitle("One week ahead predictions for incident cases in Poland")


scoringutils::plot_predictions(death_data %>%
                                 dplyr::filter(horizon == 1, 
                                               location_name == "Germany"),
                               x = "target_end_date", 
                               facet_formula = ~ model, 
                               scales = "fixed") + 
  ggplot2::ggtitle("One week ahead predictions for incident deaths in Germany")


scoringutils::plot_predictions(death_data %>%
                                 dplyr::filter(horizon == 1, 
                                               location_name == "Poland"),
                               x = "target_end_date", 
                               facet_formula = ~ model, 
                               scales = "fixed") + 
  ggplot2::ggtitle("One week ahead predictions for incident deaths in Poland")

```



## Score Overview

Overview of all the models and metrics

``` {r fig.show = "hold", out.width = "100%"}
scores_cases <- scoringutils::eval_forecasts(case_data,
                                             summarise_by = "model")

scores_deaths <- scoringutils::eval_forecasts(death_data,
                                              summarise_by = "model")


scoringutils::score_table(scores_cases) + 
  ggplot2::ggtitle("Incident Cases")

scoringutils::score_table(scores_deaths) +
  ggplot2::ggtitle("Incident Deaths")


```

## Interval Score Components

Weighted interval score broken down into its components "overprediction penalty", 
"underprediction penalty" and "sharpness"

``` {r out.width = "100%"}
scoringutils::wis_components(scores_cases, x = "model")  +
  ggplot2::labs(title = "Incident Cases")

scoringutils::wis_components(scores_deaths, x = "model")  +
  ggplot2::labs(title = "Incident Cases")
```


## Calibration

### Interval Coverage
Plot of the percentage of true values captured by each prediction interval

``` {r}
scores_cases <- scoringutils::eval_forecasts(case_data,
                                             summarise_by = c("model", "range"))

scores_deaths <- scoringutils::eval_forecasts(death_data,
                                              summarise_by = c("model", "range"))


scoringutils::interval_coverage(scores_cases, 
                                facet_formula = ~ model) + 
  ggplot2::ggtitle("Incident Cases")

scoringutils::interval_coverage(scores_deaths, 
                                facet_formula = ~ model) +
  ggplot2::ggtitle("Incident Deaths")


```



### Quantile Coverage
Plot of the percentage of true values below each predictive quantile level

``` {r}

scoringutils::quantile_coverage(case_data, 
                                facet_formula = ~ model) +
  ggplot2::ggtitle("Incident Cases")

scoringutils::quantile_coverage(death_data, 
                                facet_formula = ~ model) +
  ggplot2::ggtitle("Incident Deaths")
  
```


## Bias 

``` {r}

scores_cases <- scoringutils::eval_forecasts(case_data,
                                             summarise_by = c("model", 
                                                              "location_name"))

scores_deaths <- scoringutils::eval_forecasts(death_data,
                                              summarise_by = c("model", 
                                                              "location_name"))


scoringutils::score_heatmap(scores_cases, metric = "bias", 
                            x = "location_name") +
  ggplot2::ggtitle("Incident Cases")


scoringutils::score_heatmap(scores_deaths, metric = "bias", 
                            x = "location_name") +
  ggplot2::ggtitle("Incident Deaths")

```




